% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\section*{附录：参考文献条目（文本版）}
\begin{enumerate}
  \item 唐岸达, 林宙辰. 大模型参数高效微调方法综述: 技术、趋势与挑战[J/OL]. 自动化学报, 2026.
  \item Han Z, Gao C, Liu J, Zhang J, Zhang S Q. Parameter-Efficient Fine-Tuning for Large Models: A Comprehensive Survey, 2024.
  \item Wang L, Chen S, Jiang L, 等. Parameter-efficient fine-tuning in large language models: a survey of methodologies, 2025.
  \item Houlsby N, Giurgiu A, Jastrzebski S, 等. Parameter-Efficient Transfer Learning for NLP, ICML 2019.
  \item Li X L, Liang P. Prefix-Tuning: Optimizing Continuous Prompts for Generation, ACL 2021.
  \item Hu E J, Shen Y, Wallis P, 等. LoRA: Low-Rank Adaptation of Large Language Models, ICLR 2022.
  \item Zhang Q, Chen M, Bukharin A, 等. AdaLoRA, ICLR 2023.
  \item Dettmers T, Pagnoni A, Holtzman A, Zettlemoyer L. QLoRA, NeurIPS 2023.
  \item Zhou Z, Wei X, Zhang J, Sun G. PetS, USENIX ATC 2022.
  \item Chen L, Ye Z, Wu Y, 等. Punica: Multi-Tenant LoRA Serving, MLSys 2024.
  \item Sheng Y, Cao S, Li D, 等. S-LoRA, MLSys 2024.
  \item Wu B, Zhu R, Zhang Z, 等. dLoRA, OSDI 2024.
  \item Li S, Lu H, Wu T, 等. Toppings, USENIX ATC 2025.
  \item Kwon W, Li Z, Zhuang S, 等. PagedAttention, SOSP 2023.
  \item Yu G I, Jeong J S, Kim G W, Kim S, Chun B G. Orca, OSDI 2022.
  \item Li Z, Zheng L, Zhong Y, 等. AlpaServe, OSDI 2023.
  \item Agrawal A, Kedia N, Panwar A, 等. Sarathi-Serve, OSDI 2024.
  \item Patel P, Choukse E, Zhang C, 等. Splitwise, ISCA 2024.
  \item Megiddo N, Modha D S. ARC, FAST 2003.
  \item Einziger G, Friedman R, Manes B. TinyLFU, TOS 2017.
  \item Beckmann N, Chen H, Cidon A. LHD, NSDI 2018.
  \item Vietri G, Rodriguez L V, Martinez W A, 等. LeCaR, HotStorage 2018.
  \item Song Z, Berger D S, Li K, Lloyd W. LRB, NSDI 2020.
  \item Yang D, Berger D S, Li K, Lloyd W. A Learned Cache Eviction Framework with Minimal Overhead, 2023.
  \item Zhou Z, Ning X, Hong K, 等. A Survey on Efficient Inference for Large Language Models, 2024.
  \item Pan J, Li G. A Survey of LLM Inference Systems, 2025.
  \item Yang D, Li A, Li K, Lloyd W. Learned Prefix Caching for Efficient LLM Inference, 2025.
\end{enumerate}
